Error Reporting Parsers: a Monad Transformer Approach

### 2013-05-26 article.tex
Fix quote
Signed-off-by: Edward Z. Yang <ezyang@mit.edu>

\begin{introduction}
Parsing is "the process of analysing a string of symbols according to the rules
of a formal grammar" \cite{wikipedia_parsing}, with the general goal of building 
a tree representing the structure of the parsed input, upon which further 
operations such as interpretation or code generation are then performed.

>>>>

\begin{introduction}
Parsing is ``the process of analysing a string of symbols according to the rules
of a formal grammar" \cite{wikipedia_parsing}, with the general goal of building 
a tree representing the structure of the parsed input, upon which further 
operations such as interpretation or code generation are then performed.
